Scottish Child Poverty Briefing Plots

### 2024-06-18 minos/outcomes/ChildPovReduction_Combined.Rmd
More plots and improvements in ChildPovertyReduction plotting scripts;

  summary_group <- paste0(summary_group, '_income_quint2')

@@

@@

>>>>

  summary_group <- paste0(summary_group, '_income_quint')

@@

```{r "synthpop_uncertainty_plot", include=FALSE}
synthpop_uncertainty <- function(summary_group, scen, var) {
  # summary_group <- 'whole_pop'
  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'

  #data$pop_sample <- mutate(data, pop_sample = ceiling(run_id / 10))

  data <- data %>%
    select(run_id, .data[[var]], mean_cost, year, scen) %>%
    mutate(pop_sample = ceiling(run_id / 10))

  plot_data_local <- data %>%
    group_by(pop_sample, year) %>%
    summarise(var_mean = mean(.data[[var]]))

  plot_data_global <- data %>%
    group_by(year) %>%
    summarise(global_var_mean = mean(.data[[var]]))

  p1 <- ggplot(plot_data_local, aes(x = year, y = var_mean)) +
    geom_line(aes(group = pop_sample), alpha = 0.4) +
    geom_line(data = plot_data_global, aes(x = year, y = global_var_mean), color = 'red') +
    labs(title = paste0(var, ' uncertainty in Synthetic Population Sample'),
         subtitle = 'Global mean (red) vs local means (grey)') +
    xlab('Year') +
    ylab(paste0('Mean ', var))

  print(p1)
}
```

@@

# SAMPLE UNCERTAINTY

When running MINOS with a synthetic population, due to the size of the synthetic populations and the demands of the model, we have to take a reduced sample as our starting population. For the Scotland synthetic runs we take a 10% sample, which reduces the population size from roughly 5.5m to 550,000.

We therefore have to also account for the uncertainty in model outputs that comes from this reduced sample. As a somewhat temporary fix for this, we have done the following:

- Generate 10 different 10% samples from our synthetic population
  - Generate a replenishing population from each of these samples
- Use each distinct 10% sample for 10 runs each, totalling 100 runs
- Plot the local mean from each 10 run block, and the global mean from all 100 runs

```{r}
synthpop_uncertainty(summary_group = 'whole_pop',
                     scen = 'baseline',
                     var = 'hh_income')

synthpop_uncertainty(summary_group = 'whole_pop',
                     scen = 'baseline',
                     var = 'SF_12')
```

### 2024-06-18 minos/outcomes/ChildPovReduction_plots.Rmd
More plots and improvements in ChildPovertyReduction plotting scripts;

>>>>

## POPULATION SAMPLE TESTING

synthpop_uncertainty <- function(summary_group, scen, var) {
  # summary_group <- 'whole_pop'
  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'

  #data$pop_sample <- mutate(data, pop_sample = ceiling(run_id / 10))

  data <- data %>%
    select(run_id, .data[[var]], mean_cost, year, scen) %>%
    mutate(pop_sample = ceiling(run_id / 10))

  plot_data_local <- data %>%
    group_by(pop_sample, year) %>%
    summarise(var_mean = mean(.data[[var]]))

  plot_data_global <- data %>%
    group_by(year) %>%
    summarise(global_var_mean = mean(.data[[var]]))

  p1 <- ggplot(plot_data_local, aes(x = year, y = var_mean)) +
    geom_line(aes(group = pop_sample), alpha = 0.4) +
    geom_line(data = plot_data_global, aes(x = year, y = global_var_mean), color = 'red') +
    labs(title = paste0(var, ' uncertainty in Synthetic Population Sample'),
         subtitle = 'Global mean (red) vs local means (grey)') +
    xlab('Year') +
    ylab(paste0('Mean ', var))
